Model LF

### 2022-10-10 max_dp endogen stød.Rmd
Commit

@@

```{r}
# Simulate the model (following shock)
Shock_1b <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList1
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_01b = Shock_1b$simulation$max_dp
wage_01b = Shock_1b$simulation$wage
komp_r_01b = Shock_1b$simulation$komp_r
part_01b = Shock_1b$simulation$part
yk_ds_01b = Shock_1b$simulation$yk_ds
pc_ds_01b = Shock_1b$simulation$pc_ds
wage_ds_t_01b = Shock_1b$simulation$wage_ds_t
ur_ds_01b = Shock_1b$simulation$ur_ds
emp_01b = Shock_1b$simulation$emp
yd_hk_ds_01b = Shock_1b$simulation$yd_hk_ds

tilpas_pr_01b = Shock_1b$simulation$tilpas_pr
u_ds_01b = Shock_1b$simulation$u_ds
part_01b = Shock_1b$simulation$part
nben_h_01b = Shock_1b$simulation$nben_h
wage_ds_01b = Shock_1b$simulation$wage_ds
dp_person_01b = Shock_1b$simulation$dp_person
kont_h_ratio_01b = Shock_1b$simulation$kont_h_ratio

nl_g_01b = Shock_1b$simulation$nl_g

yd_hk_ds_01b = Shock_1b$simulation$yd_hk_ds
wage_gap1_01b = Shock_1b$simulation$wage_gap1
wage_gap_01b = Shock_1b$simulation$wage_gap
prod_01b = Shock_1b$simulation$prod
```

```{r}
plot(part_01b, col= "red"); lines(part_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(pc_ds_01b, col= "red"); lines(pc_ds_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(nben_h_01b, col= "red"); lines(nben_h_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(wage_ds_t_01b, col= "red"); lines(wage_ds_t_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(komp_r_01b, col= "red"); lines(komp_r_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(dp_person_01b, col= "red"); lines(dp_person_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(kont_h_ratio_01b, col= "red"); lines(kont_h_ratio_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(wage_gap1_01b, col= "red"); lines(wage_gap1_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(prod_01b, col= "red"); lines(prod_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

plot(((dp_person_01b - dp_person_00) / dp_person_00), col= "black", xlab= "Year", ylab= "% Change in avg income insurance");
legend("top", legend=c("income insurance"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()

plot(((komp_r_01b - komp_r_00) / komp_r_00), col= "black", xlab= "Year", ylab= "% Change in compensation rate");
legend("top", legend=c("compensation rate"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()
```

@@

plot(((nl_g_01b - nl_g_00)), col= "black", xlab= "Year", ylab= "Change in government net lending");
legend("top", legend=c("government net lending"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()

plot(((yd_hk_ds_01b - yd_hk_ds_00) / yd_hk_ds_00), col= "black", xlab= "Year", ylab= "% Change in households disposable income");
legend("top", legend=c("households disposable income"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()
```

@@

plot(((yk_ds_01b - yk_ds_00) / yk_ds_00), col= "black", xlab= "Year", ylab= "% Change in gdp");
legend("top", legend=c("GDP"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()

plot(((emp_01b - emp_00) / emp_00), col= "black", xlab= "Year", ylab= "% Change in employment");
legend("top", legend=c("Employment"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()
```

@@

```{r}
shock_wage_ds_model_shock=shock_wage_ds_model %>% window(start= c(2016,1))
```

>>>>

## Baseline Scenario 2

```{r}
# Define add-factor list (defining shock)
constantAdjList_bs2 <- list(

 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_bs2 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_bs2
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_bs2 = Shock_bs2$simulation$max_dp
wage_bs2 = Shock_bs2$simulation$wage
komp_r_bs2 = Shock_bs2$simulation$komp_r
part_bs2 = Shock_bs2$simulation$part
yk_ds_bs2 = Shock_bs2$simulation$yk_ds
pc_ds_bs2 = Shock_bs2$simulation$pc_ds
wage_ds_t_bs2 = Shock_bs2$simulation$wage_ds_t
ur_ds_bs2 = Shock_bs2$simulation$ur_ds
emp_bs2 = Shock_bs2$simulation$emp
yd_hk_ds_bs2 = Shock_bs2$simulation$yd_hk_ds

tilpas_pr_bs2 = Shock_bs2$simulation$tilpas_pr
u_ds_bs2 = Shock_bs2$simulation$u_ds
part_bs2 = Shock_bs2$simulation$part
nben_h_bs2 = Shock_bs2$simulation$nben_h
wage_ds_bs2 = Shock_bs2$simulation$wage_ds
dp_person_bs2 = Shock_bs2$simulation$dp_person
kont_h_ratio_bs2 = Shock_bs2$simulation$kont_h_ratio

nl_g_bs2 = Shock_bs2$simulation$nl_g

yd_hk_ds_bs2 = Shock_bs2$simulation$yd_hk_ds
wage_gap1_bs2 = Shock_bs2$simulation$wage_gap1
wage_gap_bs2 = Shock_bs2$simulation$wage_gap
prod_bs2 = Shock_bs2$simulation$prod
```

## Baseline Scenario 3

```{r}
shock_prod_model_shock=shock_prod_model %>% window(start= c(2006,3))
```

```{r}
# Define add-factor list (defining shock)
constantAdjList_bs3 <- list(

 shock_prod_model = TIMESERIES(shock_prod_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_bs3 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_bs3
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_bs3 = Shock_bs3$simulation$max_dp
wage_bs3 = Shock_bs3$simulation$wage
komp_r_bs3 = Shock_bs3$simulation$komp_r
part_bs3 = Shock_bs3$simulation$part
yk_ds_bs3 = Shock_bs3$simulation$yk_ds
pc_ds_bs3 = Shock_bs3$simulation$pc_ds
wage_ds_t_bs3 = Shock_bs3$simulation$wage_ds_t
ur_ds_bs3 = Shock_bs3$simulation$ur_ds
emp_bs3 = Shock_bs3$simulation$emp
yd_hk_ds_bs3 = Shock_bs3$simulation$yd_hk_ds

tilpas_pr_bs3 = Shock_bs3$simulation$tilpas_pr
u_ds_bs3 = Shock_bs3$simulation$u_ds
part_bs3 = Shock_bs3$simulation$part
nben_h_bs3 = Shock_bs3$simulation$nben_h
wage_ds_bs3 = Shock_bs3$simulation$wage_ds
dp_person_bs3 = Shock_bs3$simulation$dp_person
kont_h_ratio_bs3 = Shock_bs3$simulation$kont_h_ratio

nl_g_bs3 = Shock_bs3$simulation$nl_g

yd_hk_ds_bs3 = Shock_bs3$simulation$yd_hk_ds
wage_gap1_bs3 = Shock_bs3$simulation$wage_gap1
wage_gap_bs3 = Shock_bs3$simulation$wage_gap
prod_bs3 = Shock_bs3$simulation$prod
```

## Baseline Scenario 4

```{r}
# Define add-factor list (defining shock)
constantAdjList_bs4 <- list(

 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_bs4 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_bs4
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_bs4 = Shock_bs4$simulation$max_dp
wage_bs4 = Shock_bs4$simulation$wage
komp_r_bs4 = Shock_bs4$simulation$komp_r
part_bs4 = Shock_bs4$simulation$part
yk_ds_bs4 = Shock_bs4$simulation$yk_ds
pc_ds_bs4 = Shock_bs4$simulation$pc_ds
wage_ds_t_bs4 = Shock_bs4$simulation$wage_ds_t
ur_ds_bs4 = Shock_bs4$simulation$ur_ds
emp_bs4 = Shock_bs4$simulation$emp
yd_hk_ds_bs4 = Shock_bs4$simulation$yd_hk_ds

tilpas_pr_bs4 = Shock_bs4$simulation$tilpas_pr
u_ds_bs4 = Shock_bs4$simulation$u_ds
part_bs4 = Shock_bs4$simulation$part
nben_h_bs4 = Shock_bs4$simulation$nben_h
wage_ds_bs4 = Shock_bs4$simulation$wage_ds
dp_person_bs4 = Shock_bs4$simulation$dp_person
kont_h_ratio_bs4 = Shock_bs4$simulation$kont_h_ratio

nl_g_bs4 = Shock_bs4$simulation$nl_g

yd_hk_ds_bs4 = Shock_bs4$simulation$yd_hk_ds
wage_gap1_bs4 = Shock_bs4$simulation$wage_gap1
wage_gap_bs4 = Shock_bs4$simulation$wage_gap
prod_bs4 = Shock_bs4$simulation$prod
```

## Baseline Scenario 5-6

```{r}
# Define add-factor list (defining shock)
constantAdjList_bs56 <- list(

 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_prod_model = TIMESERIES(shock_prod_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_bs56 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_bs56
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_bs56 = Shock_bs56$simulation$max_dp
wage_bs56 = Shock_bs56$simulation$wage
komp_r_bs56 = Shock_bs56$simulation$komp_r
part_bs56 = Shock_bs56$simulation$part
yk_ds_bs56 = Shock_bs56$simulation$yk_ds
pc_ds_bs56 = Shock_bs56$simulation$pc_ds
wage_ds_t_bs56 = Shock_bs56$simulation$wage_ds_t
ur_ds_bs56 = Shock_bs56$simulation$ur_ds
emp_bs56 = Shock_bs56$simulation$emp
yd_hk_ds_bs56 = Shock_bs56$simulation$yd_hk_ds

tilpas_pr_bs56 = Shock_bs56$simulation$tilpas_pr
u_ds_bs56 = Shock_bs56$simulation$u_ds
part_bs56 = Shock_bs56$simulation$part
nben_h_bs56 = Shock_bs56$simulation$nben_h
wage_ds_bs56 = Shock_bs56$simulation$wage_ds
dp_person_bs56 = Shock_bs56$simulation$dp_person
kont_h_ratio_bs56 = Shock_bs56$simulation$kont_h_ratio

nl_g_bs56 = Shock_bs56$simulation$nl_g

yd_hk_ds_bs56 = Shock_bs56$simulation$yd_hk_ds
wage_gap1_bs56 = Shock_bs56$simulation$wage_gap1
wage_gap_bs56 = Shock_bs56$simulation$wage_gap
prod_bs56 = Shock_bs56$simulation$prod
```

@@

```{r}
# Simulate the model (following shock)
Shock_1 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList1
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_01 = Shock_1$simulation$max_dp
wage_01 = Shock_1$simulation$wage
komp_r_01 = Shock_1$simulation$komp_r
part_01 = Shock_1$simulation$part
yk_ds_01 = Shock_1$simulation$yk_ds
pc_ds_01 = Shock_1$simulation$pc_ds
wage_ds_t_01 = Shock_1$simulation$wage_ds_t
ur_ds_01 = Shock_1$simulation$ur_ds
emp_01 = Shock_1$simulation$emp
yd_hk_ds_01 = Shock_1$simulation$yd_hk_ds

tilpas_pr_01 = Shock_1$simulation$tilpas_pr
u_ds_01 = Shock_1$simulation$u_ds
part_01 = Shock_1$simulation$part
nben_h_01 = Shock_1$simulation$nben_h
wage_ds_01 = Shock_1$simulation$wage_ds
dp_person_01 = Shock_1$simulation$dp_person
kont_h_ratio_01 = Shock_1$simulation$kont_h_ratio

nl_g_01 = Shock_1$simulation$nl_g

yd_hk_ds_01 = Shock_1$simulation$yd_hk_ds
wage_gap1_01 = Shock_1$simulation$wage_gap1
wage_gap_01 = Shock_1$simulation$wage_gap
prod_01 = Shock_1$simulation$prod
```

```{r}
plot(part_01, col= "red"); lines(part_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(dp_person_01, col= "red"); lines(dp_person_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(kont_h_ratio_01, col= "red"); lines(kont_h_ratio_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(wage_gap1_01, col= "red"); lines(wage_gap1_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(prod_01, col= "red"); lines(prod_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

plot(((dp_person_01 - dp_person_00) / dp_person_00), col= "black", xlab= "Year", ylab= "% Change in avg income insurance");
legend("top", legend=c("income insurance"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()

plot(((komp_r_01 - komp_r_00) / komp_r_00), col= "black", xlab= "Year", ylab= "% Change in compensation rate");
legend("top", legend=c("compensation rate"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()
```

@@

plot(((nl_g_01 - nl_g_00)), col= "black", xlab= "Year", ylab= "Change in government net lending");
legend("top", legend=c("government net lending"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()

plot(((yd_hk_ds_01 - yd_hk_ds_00) / yd_hk_ds_00), col= "black", xlab= "Year", ylab= "% Change in households disposable income");
legend("top", legend=c("households disposable income"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()
```

@@

plot(((yk_ds_01 - yk_ds_00) / yk_ds_00), col= "black", xlab= "Year", ylab= "% Change in gdp");
legend("top", legend=c("GDP"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()

plot(((emp_01 - emp_00) / emp_00), col= "black", xlab= "Year", ylab= "% Change in employment");
legend("top", legend=c("Employment"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()
```

@@

```{r}
# Define add-factor list (defining shock)
constantAdjList2 <- list(

  shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_2 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList2
                    )
```

yk_ds_02 = Shock_2$simulation$yk_ds
emp_02 = Shock_2$simulation$emp
wage_ds_02 = Shock_2$simulation$wage_ds
ur_ds_02 = Shock_2$simulation$ur_ds
pc_ds_02 = Shock_2$simulation$pc_ds
yd_hk_ds_02 = Shock_2$simulation$yd_hk_ds
pconk_ds_02 = Shock_2$simulation$pconk_ds
komp_r_02 = Shock_2$simulation$komp_r
max_dp_02 = Shock_2$simulation$max_dp
nben_h_02 = Shock_2$simulation$nben_h
yd_hk_ds_02 = Shock_2$simulation$yd_hk_ds
ik_02 = Shock_2$simulation$ik
wage_ds_t_02 = Shock_2$simulation$wage_ds_t
nben_h_un_02 = Shock_2$simulation$nben_h_un
nl_g_02 = Shock_2$simulation$nl_g
nsben_h_02 = Shock_2$simulation$nsben_h
dp_person_02 = Shock_2$simulation$dp_person
xk_ds_02 = Shock_2$simulation$xk_ds
mk_ds_02 = Shock_2$simulation$mk_ds
ik_02 = Shock_2$simulation$ik
rer_02 = Shock_2$simulation$rer
ps_ds_02 = Shock_2$simulation$ps_ds
i_bd_nfc_k_ds_02 = Shock_2$simulation$i_bd_nfc_k_ds
yd1_hk_ds_02 = Shock_2$simulation$yd1_hk_ds
yd2a_hk_ds_02 = Shock_2$simulation$yd2a_hk_ds
yd2b_hk_02 = Shock_2$simulation$yd2b_hk

i_equip_nfc_k_ds_02 = Shock_2$simulation$i_equip_nfc_k_ds
u_ds_02 = Shock_2$simulation$u_ds
wage_gap1_02 = Shock_2$simulation$wage_gap1
gk_02 = Shock_2$simulation$gk
kont_h_ratio_02 = Shock_2$simulation$kont_h_ratio

wage_gap_02 = Shock_2$simulation$wage_gap
max_gap_02 = Shock_2$simulation$max_gap

inflation_02 = Shock_2$simulation$inflation
prod_02 = Shock_2$simulation$prod

net_balance_02= xk_ds_02 - mk_ds_02

```{r}
plot(max_dp_02, col= "red"); lines(max_dp_bs2, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(i_bd_nfc_k_ds_02, col= "red"); lines(i_bd_nfc_k_ds_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(dp_person_02, col= "red"); lines(dp_person_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(yk_ds_02, col= "red"); lines(yk_ds_bs2, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(wage_ds_t_02, col= "red"); lines(wage_ds_t_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(i_equip_nfc_k_ds_02, col= "red"); lines(i_equip_nfc_k_ds_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(ps_ds_02, col= "red"); lines(ps_ds_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(yd1_hk_ds_02, col= "red"); lines(yd1_hk_ds_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(pconk_ds_02, col= "red"); lines(pconk_ds_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(gk_02, col= "red"); lines(gk_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(u_ds_02, col= "red"); lines(u_ds_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(wage_gap1_02, col= "red"); lines(wage_gap1_01, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(wage_gap_02, col= "red"); lines(wage_gap_01, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(prod_02, col= "red"); lines(prod_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(((wage_ds_t_02 - wage_ds_t_bs2) / wage_ds_t_bs2), col= "black", xlab= "Year", ylab= "% Change in Target wage", main= "Target Wage");
grid()

plot((wage_gap_02), col= "black", xlab= "Year", ylab= "Wage gap as % of target wage", main= "Wage gap");
grid()
```

plot(((wage_ds_02 - wage_ds_00) / wage_ds_00), col= "black", xlab= "Year", ylab= "% Change in wages", main= "Wages");
grid()

plot(((pc_ds_02 - pc_ds_00) / pc_ds_00), col= "black", xlab= "Year", ylab= "% Change in consumer prices", main= "Consumer prices");
grid()
```

```{r}
plot(((net_balance_02 - net_balance_00) / net_balance_00), col= "black", xlab= "Year", ylab= "% Change in the net balance", main= "Net balance");
grid()
```

plot(((pconk_ds_02 - pconk_ds_00) / pconk_ds_00), col= "black", xlab= "Year", ylab= "% Change in consumption", main= "Consumption");
grid()

plot(((ik_02 - ik_00) / ik_00), col= "black", xlab= "Year", ylab= "% Change in investments", main= "Investment");
grid()
```

plot(((yk_ds_02 - yk_ds_00) / yk_ds_00), col= "black", xlab= "Year", ylab= "% Change in gdp", main= "GDP");

plot(((emp_02 - emp_00) / emp_00), col= "black", xlab= "Year", ylab= "% Change in employment", main= "Employment");
grid()
```

```{r}
# Define add-factor list (defining shock)
constantAdjList_3 <- list(

  shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_prod_model = TIMESERIES(shock_prod_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_3 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_3
                    )
```

yk_ds_03 = Shock_3$simulation$yk_ds
emp_03 = Shock_3$simulation$emp
wage_ds_03 = Shock_3$simulation$wage_ds
ur_ds_03 = Shock_3$simulation$ur_ds
pc_ds_03 = Shock_3$simulation$pc_ds
yd_hk_ds_03 = Shock_3$simulation$yd_hk_ds
pconk_ds_03 = Shock_3$simulation$pconk_ds
komp_r_03 = Shock_3$simulation$komp_r
max_dp_03 = Shock_3$simulation$max_dp
nben_h_03 = Shock_3$simulation$nben_h
yd_hk_ds_03 = Shock_3$simulation$yd_hk_ds
ik_03 = Shock_3$simulation$ik
wage_ds_t_03 = Shock_3$simulation$wage_ds_t
nben_h_un_03 = Shock_3$simulation$nben_h_un
nl_g_03 = Shock_3$simulation$nl_g
nsben_h_03 = Shock_3$simulation$nsben_h
dp_person_03 = Shock_3$simulation$dp_person
part1_03 = Shock_3$simulation$part1
u_ds_03 = Shock_3$simulation$u_ds
kont_h_ratio_03 = Shock_3$simulation$kont_h_ratio
part_03 = Shock_3$simulation$part

rw_ds_03 = Shock_3$simulation$rw_ds
kuld_03 = Shock_3$simulation$shock_kuld
```

plot(yk_ds_03, col= "red"); lines(yk_ds_bs3, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(wage_ds_t_03, col= "red"); lines(wage_ds_t_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(ur_ds_03, col= "red"); lines(ur_ds_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(part1_03, col= "red"); lines(part1_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(emp_03, col= "red"); lines(emp_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(komp_r_03, col= "red"); lines(komp_r_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(u_ds_03, col= "red"); lines(u_ds_02, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(kont_h_ratio_03, col= "red"); lines(kont_h_ratio_02, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

plot(((yk_ds_03 - yk_ds_bs3) / yk_ds_bs3), col= "black", xlab= "Year", ylab= "% Change in Gdp", main= "Gdp")

plot(((ur_ds_03 - ur_ds_bs3) / ur_ds_bs3), col= "black", xlab= "Year", ylab= "Wage gap as % of target wage", main= "Wage gap");
grid()
```

## Scenario 4 reg kuld

  shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q')

yk_ds_04 = Shock_4$simulation$yk_ds
emp_04 = Shock_4$simulation$emp
wage_ds_04 = Shock_4$simulation$wage_ds
ur_ds_04 = Shock_4$simulation$ur_ds
pc_ds_04 = Shock_4$simulation$pc_ds
yd_hk_ds_04 = Shock_4$simulation$yd_hk_ds
pconk_ds_04 = Shock_4$simulation$pconk_ds
komp_r_04 = Shock_4$simulation$komp_r
max_dp_04 = Shock_4$simulation$max_dp
nben_h_04 = Shock_4$simulation$nben_h
yd_hk_ds_04 = Shock_4$simulation$yd_hk_ds
ik_04 = Shock_4$simulation$ik
wage_ds_t_04 = Shock_4$simulation$wage_ds_t
nben_h_un_04 = Shock_4$simulation$nben_h_un
nl_g_04 = Shock_4$simulation$nl_g
nsben_h_04 = Shock_4$simulation$nsben_h
dp_person_04 = Shock_4$simulation$dp_person
part1_04 = Shock_4$simulation$part1
u_ds_04 = Shock_4$simulation$u_ds
kont_h_ratio_04 = Shock_4$simulation$kont_h_ratio
part_04 = Shock_4$simulation$part

rw_ds_04 = Shock_4$simulation$rw_ds
kuld_04 = Shock_4$simulation$shock_kuld
```

plot(yk_ds_04, col= "red"); lines(yk_ds_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(wage_ds_t_04, col= "red"); lines(wage_ds_t_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(ur_ds_04, col= "red"); lines(ur_ds_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(part1_04, col= "red"); lines(part1_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(emp_04, col= "red"); lines(emp_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(komp_r_04, col= "red"); lines(komp_r_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(u_ds_04, col= "red"); lines(u_ds_02, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(kont_h_ratio_04, col= "red"); lines(kont_h_ratio_02, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

plot(((nl_g_04 - nl_g_bs4)), col= "black", xlab= "Year", ylab= "changes in government net lending", main= "government net lending", ylim= c(-500,1500));
lines(((nl_g_01 - nl_g_00)), col= "red");
legend("left", legend=c("Scenario 3","Scenairo 2"),
       lty=c(1),lwd=c(2),bty="n", col = c("black","red"));
grid()

plot(((nben_h_04 - nben_h_bs4) / nben_h_bs4), col= "black", xlab= "Year", ylab= "% changes in net benefits HH", main= "Net benefits HH");
lines(((nben_h_01 - nben_h_00) / nben_h_00), col= "red");
legend("left", legend=c("Scenario 3","Scenairo 2"),
       lty=c(1),lwd=c(2),bty="n", col = c("black","red"));
grid()
```

plot(((yk_ds_04 - yk_ds_bs4) / yk_ds_bs4), col= "black", xlab= "Year", ylab= "% Change in Gdp", main= "Gdp");
lines(((yk_ds_01 - yk_ds_00) / yk_ds_00), col= "red");
legend("left", legend=c("Scenario 3","Scenairo 2"),
       lty=c(1),lwd=c(2),bty="n", col = c("black","red"));
grid()

plot(((ur_ds_04 - ur_ds_bs4) / ur_ds_bs4), col= "black", xlab= "Year", ylab= "Wage gap as % of target wage", main= "Wage gap");
grid()
```

plot(((emp_04 - emp_bs4) / emp_bs4), col= "black", xlab= "Year", ylab= "% Change in Employment", main= "Employment");
lines(((emp_01 - emp_00) / emp_00), col= "red");
legend("left", legend=c("Scenario 3","Scenairo 2"),
       lty=c(1),lwd=c(2),bty="n", col = c("black","red"));
grid()
